---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# OSPSuite.Addins

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/OSPSuite.Addins)](https://CRAN.R-project.org/package=OSPSuite.Addins)
<!-- badges: end -->

The goal of `{ospsuite.addins}` is to provide RStudio addins to work with the Open System Pharmacology ecosystem.

## Installation

You can install the development version of OSPSuite.Addins from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("pchelle/OSPSuite.Addins")
```

> [!IMPORTANT]
> Once installed, you will need to restart RStudio to see the functions from `{ospsuite.addins}` in the Addins list.

## Examples

### Get all OSPSuite dimensions and units

To get a datatable of all the OSPSuite dimensions and units, you can use the following code:

```{r example-table-of-units, eval=FALSE}
ospsuite.addins::tableOfUnits()
```

> [!TIP]
> You can also go to the Addins menu in RStudio and select "__View OSP Units__".

### Get all OSPSuite PK Parameters, their dimensions and units

To get a datatable of all the OSPSuite PK Parameters, their dimensions and units, you can use the following code:

```{r example-table-of-pk, eval=FALSE}
ospsuite.addins::tableOfPKParameters()
```

> [!TIP]
> You can also go to the Addins menu in RStudio and select "__View PK Parameters__".
